---
title: "HW3"
author: "Chen Mo"
date: "10/7/2020"
output: github_document
---
Load the library
```{r}
library(tidyverse)
library(p8105.datasets)
```

Define the setup:
```{r}
knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

#Problem 1  
Load the data:
```{r}
data("instacart")
```
This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. 

Observations are the level of items in orders by user. There are user / order variables -- user ID, order ID, order day, and order hour. There are also item variables -- name, aisle, department, and some numeric codes.

question 1: how many aisles & which aisles are the most items ordered from?
```{r}
aisle_df =
instacart  %>% 
        count(aisle) %>% 
        arrange(desc(n))
```
There are `r nrow(aisle_df)` aisles and fresh vegetables is the most item ordered from.

question 2: make a plot that shows the number of items ordered in each aisle.
```{r}
instacart %>% 
        count(aisle) %>% 
        filter(n > 10000) %>% 
        mutate(
                aisle = factor(aisle),
                aisle = fct_reorder(aisle, n)
        ) %>% 
        ggplot(aes(x = aisle, y = n)) +
        geom_point() +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

question 3: make a table showing the three most popular items in each of the aisles:
```{r}
instacart %>% 
	filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
        group_by(aisle) %>% 
        count(product_name) %>% 
        mutate(rank = min_rank(desc(n))) %>%
        filter(rank < 4) %>%
        arrange(aisle,rank) %>% 
        knitr::kable()
```

question 4: make a table showing the mean hour of the day:
```{r}
instacart %>% 
        filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
        group_by(product_name, order_dow) %>% 
        summarise(mean_hour_of_day = mean(order_hour_of_day)) %>% 
        pivot_wider(
                names_from = order_dow,
                values_from = mean_hour_of_day
                    ) %>% 
        knitr::kable()
```

